---
title: "count_last_consecutive_signs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{count_last_consecutive_signs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scr2)
```

## Parameters
Count_last_consecutive_signs() function holds the following parameters:

- ticker: This is the ticker symbol for a stock.

- start and end: These parameters set the time frame for the analysis. The function will only consider returns within this period.

- frequency: This parameter allows to specify the frequency of returns. For example, if you set frequency = "daily", the function will consider daily returns.

## Usage

Inserire esempio qualunque codice

The Count_last_consecutive_signs() function provides insight into the most recent trend of a stock. If the function returns a high number, this indicates that the stock has had a series of consecutive returns with the same sign, suggesting a strong current upward or downward trend.

For example, if the last returns up until the end of the period are ordered as follows: positive, negative, negative, and negative, the output will be 3, as there are three last returns with the same (negative) sign.
