---
title: "number_consecutive_returns"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{number_consecutive_returns}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scr2)
```


## Parameters

Parameters accepted by Number_consecutive_returns():

- n: This parameter represents the number of consecutive returns of interest. For example, if n = 3, the function will look for occurrences where the stock had 3 consecutive positive or negative returns.

- ticker: This is the ticker symbol of a stock of your choice.

- start and end: These parameters define the time horizon for the analysis. The function will only consider returns that occurred between these dates.

- frequency: This parameter represents the frequency of returns that should be considered. For instance, if frequency = "daily", the function will consider daily returns.

- positive: This parameter determines whether the function should count positive or negative returns. If positive = TRUE, the function will count consecutive positive returns; if positive = FALSE, it will count consecutive negative returns.

## Usage

esempio codice

The Number_consecutive_returns() function can be used to look for historical patterns of a stock's returns and analyze market behavior over the chosen time-frame. For example, a high number of consecutive positive returns could suggest a strong bullish trend, while a high number of consecutive negative returns could indicate a bearish trend.

By adjusting the parameters, you can customize the function to suit your analytical needs. For instance, you can set n to track long streaks of returns or change frequency to analyze weekly or monthly returns instead of daily returns.
