---
title: "probability_consecutive_returns"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{probability_consecutive_returns}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scr2)
```


## Parameters

Parameters for the Probability_consecutive_returns() function:

- n: This represents the number of consecutive returns of interest. For example, if you set n = 3, the function will compute the historical probability of the selected stock experiencing 3 consecutive positive or negative returns.

- ticker: This is the ticker symbol of a stock of your choice.

- start and end: These define the time period for the analysis. The function will only consider returns that occurred between these dates.

- frequency: This parameter represents the frequency of returns to consider. For example, if frequency = "daily", the function will compute the probability based on daily returns.

- positive: This parameter determines whether the function should consider positive or negative returns. If positive = TRUE, the function will compute the probability of consecutive positive returns; if positive = FALSE, it will compute the probability of consecutive negative returns.

## Usage

esempio codice

The Probability_consecutive_returns() function provides the historical probability of consecutive positive or negative returns, it allows to gain insights into the potential future performance of a stock.

For example, a high probability of consecutive positive returns could be an indicator of a strong stock, whereas a high probability of consecutive negative returns could indicate riskier investments.
